Measuring individual differences in the understanding of gaze cues

### 2023-03-10 paper/manuscript.Rmd
prepare repo for revision

affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
authornote: |
abstract: |
  Traditional measures of social cognition used in developmental research often lack satisfactory psychometric properties and are not designed to capture variation *between* individuals. 
  Here we present TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open); a brief (approx. 5–10min), reliable, open-source task to quantify individual differences in the understanding of gaze cues. 
   Our interactive browser-based task works across devices and enables in-person and remote testing. The implemented spatial layout allows for discrete and continuous measures of participants’ click imprecision and is easily adaptable to different study requirements. 
   Our task measures inter-individual differences in a child (N = 387) and an adult (N = 236) sample. Our two study versions and data collection modes yield comparable results that show substantial developmental gains: the older children are, the more accurately they locate the target. High internal consistency and test–retest reliability estimates underline that the captured variation is systematic. This work shows a promising way forward in studying individual differences in social cognition and will help us explore the structure and development of our core social-cognitive processes in greater detail.

keywords          : "social cognition, individual differences, gaze cues, cognitive development"
wordcount         : "6856"
bibliography      : ["../../references.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

@@

Numerous studies have already examined individual differences in social cognition [for an overview, see @hughes2015individual; @slaughter2015theorya]. These individual differences studies often focus on the relationship between social-cognitive abilities and: (1) family influences, (2) other cognitive constructs, and (3) social behavioral outcomes [for an overview, see @repacholi2003introduction]. Studies on social-cognitive abilities and family influences include the effect of parenting practices [for a review, see @pavarini2013parental], attachment quality [e.g., @astor2020social], mental state talk [@hughes2011individual; @gola2012mental; @lecce2014promoting], and family background as parental education, occupation, sibling interaction and childcare [@dunn1991young; @cutting1999theory; @bulgarelli2016social]. Another group of individual differences studies focuses on the interplay of social and physical cognition [@herrmann2010structure], executive functions [@carlson2004individual; @carlson2001individual; @buttelmann2021relations; @hughes2007executive; @benson2012individual], and language abilities [@okumura2017individual; @milligan2007language; @mcewen2007origins]. Studies on social behavioral outcomes measured the interplay of social cognition and prosociality [for a review, see @imuta2016theory; @walker2005gender], stereotypes, and resource allocations [@rizzo2018theory], and moral intentions [@sodian2016understanding].

However, developmental psychologists are frequently surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally [e.g., @sodian2016understanding]. This might be because traditional measures of social cognition are not designed to capture variation between children: they often rely on low trial numbers, small sample sizes, and dichotomous measures. A recent review showed that many studies on social cognition measures failed to report relevant psychometric properties at all [@beaudoin2020systematic] or -- when they did -- showed mixed results on test-retest reliability [@mayes1996testretest; @hughes2000good].

@@

However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value [@repacholi2003introduction]. Thus, this task seems well suited to track a particular group-level developmental transition, yet it fails to capture individual differences [cf. "reliability paradox", @hedge2018reliability].
As @wellman2012theory put it, "it's really only passing/failing one sort of understanding averaged across age" (p. 317).
This has profound implications for what studies on individual differences using this task (or others) can show.
Poor measurement of social cognition on an individual level is likely to conceal relations between different aspects of cognition and may obscure developmental change.

@@

Our goal was to design a new measure of social cognition that captures individual differences across age groups in a systematic and reliable way.
We focused on a fundamental ability implicated in many social-cognitive reasoning processes: gaze understanding -- the ability to locate and use the attentional focus of an agent.
The first component of this ability is often termed gaze following -- turning one's eyes in the same direction as the gaze of another agent -- and has been studied intensively [@itakura1998use; @delbianco2019developmental; @byers-heinlein2021development; @moore2008development; @coelho2006searching; @tomasello2007reliance; @hernik2019infant; @astor2021gaze; @frischen2007gaze; @shepherd2010following; @lee1998children].
Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a "front end ability" [@brooks2005development, p. 535].
In our definition, gaze understanding goes one step further by including the *acting on the gaze-cued location* -- therefore, using the available social information to guide one's behavior as needed in real-life conditions.

@@

To keep participants engaged and interested, the presentation of events is accompanied by cartoon-like effects.
Each trial starts with an attention-getter: an eye-blinking sound plays while the pupils and iris of the agent enlarge (increase to 130%) and change in opacity (decrease to 75%) for 0.3 sec.
The landing of the target is accompanied by a tapping sound.
Once the target landed, the instructor's voice asked "Where is the balloon?".
To confirm the participant's click, a short plop sound plays, and a small orange circle appears at the location of choice.
Participants do not receive differential feedback, so that learning effects are reduced, and trials stay comparable across the sample.
If no response is registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.

@@

We designed two study versions that differ in the target's final hiding place and, consequently, on the outcome measure: a *hedge version* (continuous) and a *box version* (discrete).
Both versions use the same first training trial and then differ in the consecutive training and test trials.
In the hedge version, participants have to indicate their estimated target location directly on a hedge.
Here, the dependent variable is imprecision, which is defined as the absolute difference between the target center and the x coordinate of the participant's click.
In the box version, the target lands in a box, and participants are asked to click on the box that hides the target.
Researchers can choose how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations.
Here, we use a categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
Note that in the test trials of both versions, the target flight is covered by a hedge.
In the hedge version, the hedge then shrinks to a minimum height required to cover the target's end location.
In the box version, the hedge shrinks completely.
The boxes then hide the target's final destination (see Figure \@ref(fig:fig1)B and C).

(ref:figlab1) **Study setup**. (A) Infrastructure for online testing. (i) Subjects aged 3 to 99+ can participate. Data collection can take place anywhere: online, in kindergartens, or in research labs. (ii) The task is presented as a website that works across devices. (iii) The scripts for the website and the recorded data are stored on secure in-house servers. (B) Hedge version (continuous) of the TANGO. (i) The agent stands in a window with the target in front of them. (ii) A hedge grows and covers the target. (iii) The target falls to a random location on the ground. The agent's eyes track the movement of the target. (C) Box version (discrete) of the TANGO. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.

@@

Task design, data collection, and sample sizes were pre-registered: <https://osf.io/snju6> (child sample) and <https://osf.io/r3bhn> (adult sample).
The analyses reported here were not pre-registered but followed the structure of the ones specified in the above pre-registrations.
The additional analyses mentioned in the pre-registrations (e.g., computational model) will be reported elsewhere.

@@

```{r vali_sample}
vali <- testtrials %>% 
  filter(studytype == "vali" & (ageInYears < 6 | ageInYears == 18))

vali_kids <- vali %>%
  filter(ageInYears < 6) %>% 
  group_by(datacollection, ageInYears) %>%
  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
  summarise(
    nTotal = n_distinct(subjID), 
    meanAgeInMonths = mean(ageInMonths, na.rm = T) %>% round(2),
    sdAgeInMonths = sd(ageInMonths, na.rm = T) %>% round(2),
    minAgeInMonths = min(ageInMonths, na.rm = T),
    maxAgeInMonths = max(ageInMonths, na.rm = T),
    nFemales = ceiling(sum(female/15)),
  )

vali_adults <- vali %>%
  filter(ageInYears == 18) %>% 
  ungroup() %>% 
  mutate(
    gender = ifelse(is.na(gender), 0, paste(gender)), 
    female = ifelse(gender == "f", 1, 0),
  ) %>% 
  summarise(
    nTotal = n_distinct(subjID), 
    meanAge = mean(age, na.rm = T) %>% round(2),
    sdAge = sd(age, na.rm = T) %>% round(2),
    minAge = min(age, na.rm = T),
    maxAge = max(age, na.rm = T),
    nFemales = ceiling(sum(female/15)),
  )
```

@@

We collected data from an in-person child sample, a remote child sample, and a remote adult sample.
In-person testing with children took place in kindergartens in Leipzig, Germany.
The in-person child sample consisted of `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised"])` children, including `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` 3-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "3"])` girls), `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` 4-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "4"])` girls), and `r sum(vali_kids$nTotal[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` 5-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "in-person - supervised" & vali_kids$ageInYears == "5"])` girls).

We pre-registered the replacement for participants that finished fewer than four test trials.
This was not the case for any participant.
One child stopped participation after 16 trials (i.e., 3 test trials missing) but was included in the sample due to the pre-registered replacement rule.
Two additional participants were recruited but not included in the study because the participant did not feel comfortable interacting with the tablet alone (n = 1), or due to an originally miscalculated age of the child (n = 1).

@@

The remote child sample included `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised"])` children, including `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` 3-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "3"])` girls), `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` 4-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "4"])` girls), and `r sum(vali_kids$nTotal[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` 5-year-olds (mean = `r sum(vali_kids$meanAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` months, SD = `r sum(vali_kids$sdAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, range = `r sum(vali_kids$minAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` - `r sum(vali_kids$maxAgeInMonths[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])`, `r sum(vali_kids$nFemales[vali_kids$datacollection == "remote - unsupervised" & vali_kids$ageInYears == "5"])` girls).
Of these, three families participated twice.
In these cases, we only kept the data sets from the first participation.

@@

Children in our sample grow up in an industrialized, urban Central-European context.
Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.

Adults were recruited via *Prolific* [@palan2018prolific].
*Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool.
`r vali_adults$nTotal` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females) were included.
For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour; see Supplements for further detail).

@@

All participants received 15 test trials.
In the box version, we decided to adjust the task difficulty according to the sample: children were presented with five boxes while adults were presented with eight boxes as possible target locations.

@@

@@

For test-retest reliability, we show the association between raw performance scores of the two test days and corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)D, E, I and J.[^2]

>>>>

affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
authornote: |
abstract: |
  Traditional measures of social cognition used in developmental research often lack satisfactory psychometric properties and are not designed to capture variation *between* individuals. 
  Here we present TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open); a brief (approx. 5–10min), reliable, open-source task to quantify individual differences in the understanding of gaze cues. Localizing the attentional focus of an agent is crucial in inferring their mental states, building common ground, and thus, supporting cooperation.
   Our interactive browser-based task works across devices and enables in-person and remote testing. The implemented spatial layout allows for discrete and continuous measures of participants’ click imprecision and is easily adaptable to different study requirements. 
   Our task measures inter-individual differences in a child (N = 387) and an adult (N = 236) sample. Our two study versions and data collection modes yield comparable results that show substantial developmental gains: the older children are, the more accurately they locate the target. High internal consistency and test–retest reliability estimates underline that the captured variation is systematic. This work shows a promising way forward in studying individual differences in social cognition and will help us explore the structure and development of our core social-cognitive processes in greater detail.

keywords          : "social cognition, individual differences, gaze cues, cognitive development"
wordcount         : "8548"
bibliography      : ["../../references.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa7"
classoption       : "man"
output            : papaja::apa6_word
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

@@

Numerous studies have already examined individual differences in social cognition [for an overview, see @hughes2015individual; @slaughter2015theorya].
The most common, recurring research questions are concerned with the developmental sequence of social-cognitive abilities [e.g., @wellman2004scaling], and which factors drive the development of social cognition [e.g., @gola2012mental; @devine2018family].
For example, Okumura and colleagues asked how early gaze-following and object processing relate to later language development [@okumura2017individual].
In general, individual differences studies often focus on the relationship between social-cognitive abilities and: (1) family influences, (2) other cognitive constructs, and (3) social behavioral outcomes [for an overview, see @repacholi2003introduction].
Studies on social-cognitive abilities and family influences include the effect of parenting practices [for a review, see @pavarini2013parental], attachment quality [e.g., @astor2020social], mental state talk [@hughes2011individual; @gola2012mental; @lecce2014promoting], and family background as parental education, occupation, sibling interaction and childcare [@dunn1991young; @cutting1999theory; @bulgarelli2016social].
Another group of individual differences studies focuses on the interplay of social and physical cognition [@herrmann2010structure], executive functions [@carlson2004individual; @carlson2001individual; @buttelmann2021relations; @hughes2007executive; @benson2012individual], and language abilities [@okumura2017individual; @milligan2007language; @mcewen2007origins].
Studies on social behavioral outcomes measured the interplay of social cognition and prosociality [for a review, see @imuta2016theory; @walker2005gender], stereotypes, and resource allocations [@rizzo2018theory], and moral intentions [@sodian2016understanding].

However, developmental psychologists are frequently surprised to find minor or no association between measures of social cognition that are thought to be theoretically related -- cross-sectionally and/or longitudinally [e.g., @poulin-dubois2023discontinuity; @sodian2023reply; @sodian2016understanding].
This might be because traditional measures of social cognition are not designed to capture variation between children: they often rely on low trial numbers, small sample sizes, and dichotomous measures.
A recent review showed that many studies on social cognition measures failed to report relevant psychometric properties at all [@beaudoin2020systematic] or -- when they did -- showed mixed results on test-retest reliability [@mayes1996testretest; @hughes2000good].

@@

However, from this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value [@repacholi2003introduction].
Thus, this task seems well suited to track a particular group-level developmental transition, yet it fails to capture individual differences [cf. "reliability paradox", @hedge2018reliability].
As @wellman2012theory put it, "it's really only passing/failing one sort of understanding averaged across age" (p. 317).
This has profound implications for what studies on individual differences using this task (or others) can show.
Poor measurement of social cognition on an individual level is likely to conceal relations between different aspects of cognition and may obscure developmental change.
For example, @sodian2016understanding neither found a correlation between two moral Theory of Mind False Belief and Intention tasks at 60 months, nor a relationship between these two factors and implicit False Belief understanding at 18 months.

The "Sandbox task" is one of the few tasks that attempt to overcome these methodological challenges [@begeer2012continuous; @bernstein2011theory; @coburn2015new; @mahy2017testing; @sommerville2013measuring].
This continuous FB task measures the degree to which the estimate of another's belief is biased by one's own knowledge.
Recent work questions the interpretation of this measure [@samuel2018egocentric; @samuel2018unreliability]: it is unclear whether a smaller egocentric bias can be directly translated into a better mental state reasoning ability.
Another evaluation criterion should, therefore, be whether a task captures meaningful variability in performance; that is, differences in test scores should correspond to differences in the social-cognitive ability in question.

@@

Our goal was to design a new measure of social cognition that captures individual differences across age groups in a systematic and reliable way.
We focused on a fundamental ability implicated in many social-cognitive reasoning processes: gaze understanding -- the ability to locate and use the attentional focus of an agent.
The first component of this ability is often termed gaze following -- turning one's eyes in the same direction as the gaze of another agent -- and has been studied intensively [@itakura1998use; @delbianco2019developmental; @byers-heinlein2021development; @moore2008development; @coelho2006searching; @tomasello2007reliance; @hernik2019infant; @astor2021gaze; @frischen2007gaze; @shepherd2010following; @lee1998children].
In our definition, gaze understanding goes one step further by including the *acting on the gaze-cued location* -- therefore, using the available social information to guide one's behavior as needed in real-life conditions.

Following an agent's gaze provides insights into their intentions, thoughts, and feelings by acting as a "front end ability" [@brooks2005development, p. 535].
Gaze is integral for many more sophisticated social-cognitive abilities, for example, inferences about knowledge states.
As such, the eyes have been regarded as a "window into the mind" [@shepherd2010following].
Monitoring another's attention also supports building a common ground, which is important for action coordination and cooperative social interactions [@tomasello2007reliance; @bohn2018common].
In addition, gaze and language development seem to be related [@brooks2005development].
Gaze facilitates word learning by helping to identify the referent of a new word and has been regarded as a crucial signal of nonverbal communication [@macdonald2013eye; @hernik2019infant].
While the emergence of gaze following has been well established, less is known about the developmental trajectory throughout childhood and adolescence.
One possibility is that our social-cognitive ability in question is fully developed once emerged in infancy.
However, many cognitive abilities continue to develop beyond early childhood [e.g., @gathercole2004structure for working memory; @raviv2018developmental for visual statistical learning].
Therefore, children could potentially improve in understanding gaze, fine-tuning the performance of the already existing skill.
Consequently, we aimed to assess the differentiation of the ability to understand gaze.
Our goal was not to establish the youngest age at which children understand gaze cues.
Rather, we wanted to examine how that ability changes with age.
To accurately measure developmental change, we were interested in capturing individual variability.

@@

To keep participants engaged and interested, the presentation of events is accompanied by cartoon-like effects.
Each trial starts with an attention-getter: an eye-blinking sound plays while the pupils and iris of the agent enlarge (increase to 130%) and change in opacity (decrease to 75%) for 0.3 sec.
The landing of the target is accompanied by a tapping sound.
Once the target landed, the instructor's voice asked "Where is the balloon?".
To confirm the participant's click, a short plop sound plays, and a small orange circle appears at the location of choice.
Participants do not receive differential feedback so that learning effects are reduced, and trials stay comparable across the sample.
If no response is registered within 5 secs after the target landed, an audio prompt reminds the participant to respond.

@@

We designed two study versions that differ in the target's final hiding place and, consequently, in the outcome measure: a *hedge version* (continuous) and a *box version* (discrete).
Both versions use the same first training trial and then differ in the consecutive training and test trials.
In the hedge version, participants have to indicate their estimated target location directly on a hedge.
Here, the dependent variable is imprecision, which is defined as the absolute difference between the target center and the x coordinate of the participant's click.
In the box version, the target lands in a box, and participants are asked to click on the box that hides the target.
Researchers can choose how many boxes are shown: one up to eight boxes can be displayed as potential hiding locations.
Here, we use a categorical outcome (i.e., which box was clicked) to calculate the proportion of correct responses.
Note that in the test trials of both versions, the target flight is covered by a hedge.
In the hedge version, the hedge then shrinks to a minimum height required to cover the target's end location.
In the box version, the hedge shrinks completely.
The boxes then hide the target's final destination (see Figure \@ref(fig:fig1)B and C).

(ref:figlab1) **Study setup**. (A) Infrastructure for online testing. (i) Subjects aged 3 to 99+ can participate. Data collection can take place anywhere: online, in kindergartens, or in research labs. (ii) The task is presented as a website that works across devices. (iii) The scripts for the website and the recorded data are stored on secure in-house servers. (B) Hedge version (continuous) of the TANGO. (i) The agent stands in a window with the target in front of them. (ii) A hedge grows and covers the target. (iii) The target falls to a random location on the ground. The agent's eyes track the movement of the target. Three exemplary target locations are shown to depict how indicative the agent's gaze cues are in determining the target's location. The transparent target is only shown for an illustrative purpose (not visible during the test). (C) Box version (discrete) of the TANGO. Number of boxes (min. 1; max. 8) as potential hiding locations can be set according to the researcher's need.

@@

Task design, data collection, and sample sizes were pre-registered: <https://osf.io/snju6> (child sample) and <https://osf.io/r3bhn> (adult sample).
The analyses reported here were not pre-registered but followed the structure of the ones specified in the above pre-registrations (see Footnotes for deviations).
The additional analyses mentioned in the pre-registrations (e.g., computational model) will be reported elsewhere.

@@

```{r inddiff_sample}
inddiff <- testtrials %>% 
  filter(studytype == "vali" & (ageInYears < 6 | ageInYears == 18))

inddiff_kids <- inddiff %>%
  filter(ageInYears < 6) %>% 
  group_by(datacollection, ageInYears) %>%
  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
  summarise(
    nTotal = n_distinct(subjID), 
    meanAgeInMonths = mean(ageInMonths, na.rm = T) %>% round(2),
    sdAgeInMonths = sd(ageInMonths, na.rm = T) %>% round(2),
    minAgeInMonths = min(ageInMonths, na.rm = T),
    maxAgeInMonths = max(ageInMonths, na.rm = T),
    nFemales = ceiling(sum(female/15)),
  )

inddiff_adults <- inddiff %>%
  filter(ageInYears == 18) %>% 
  ungroup() %>% 
  mutate(
    gender = ifelse(is.na(gender), 0, paste(gender)), 
    female = ifelse(gender == "f", 1, 0),
  ) %>% 
  summarise(
    nTotal = n_distinct(subjID), 
    meanAge = mean(age, na.rm = T) %>% round(2),
    sdAge = sd(age, na.rm = T) %>% round(2),
    minAge = min(age, na.rm = T),
    maxAge = max(age, na.rm = T),
    nFemales = ceiling(sum(female/15)),
  )
```

@@

We collected data from an in-person child sample, a remote child sample, and a remote adult sample.
In-person testing with children took place in kindergartens in Leipzig, Germany.
The in-person child sample consisted of `r sum(inddiff_kids$nTotal[inddiff_kids$datacollection == "in-person - supervised"])` children, including `r sum(inddiff_kids$nTotal[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "3"])` 3-year-olds (mean = `r sum(inddiff_kids$meanAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "3"])` months, SD = `r sum(inddiff_kids$sdAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "3"])`, range = `r sum(inddiff_kids$minAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "3"])` - `r sum(inddiff_kids$maxAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "3"])`, `r sum(inddiff_kids$nFemales[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "3"])` girls), `r sum(inddiff_kids$nTotal[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "4"])` 4-year-olds (mean = `r sum(inddiff_kids$meanAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "4"])` months, SD = `r sum(inddiff_kids$sdAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "4"])`, range = `r sum(inddiff_kids$minAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "4"])` - `r sum(inddiff_kids$maxAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "4"])`, `r sum(inddiff_kids$nFemales[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "4"])` girls), and `r sum(inddiff_kids$nTotal[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "5"])` 5-year-olds (mean = `r sum(inddiff_kids$meanAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "5"])` months, SD = `r sum(inddiff_kids$sdAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "5"])`, range = `r sum(inddiff_kids$minAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "5"])` - `r sum(inddiff_kids$maxAgeInMonths[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "5"])`, `r sum(inddiff_kids$nFemales[inddiff_kids$datacollection == "in-person - supervised" & inddiff_kids$ageInYears == "5"])` girls).

We pre-registered the replacement for participants that finished fewer than four test trials.
This was not the case for any participant.
One child stopped participation after 12 test trials but was included in the sample due to the pre-registered replacement rule.
Two additional participants were recruited but not included in the study because the participant did not feel comfortable interacting with the tablet alone (n = 1), or due to an originally miscalculated age of the child (n = 1).

@@

The remote child sample included `r sum(inddiff_kids$nTotal[inddiff_kids$datacollection == "remote - unsupervised"])` children, including `r sum(inddiff_kids$nTotal[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "3"])` 3-year-olds (mean = `r sum(inddiff_kids$meanAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "3"])` months, SD = `r sum(inddiff_kids$sdAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "3"])`, range = `r sum(inddiff_kids$minAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "3"])` - `r sum(inddiff_kids$maxAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "3"])`, `r sum(inddiff_kids$nFemales[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "3"])` girls), `r sum(inddiff_kids$nTotal[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "4"])` 4-year-olds (mean = `r sum(inddiff_kids$meanAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "4"])` months, SD = `r sum(inddiff_kids$sdAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "4"])`, range = `r sum(inddiff_kids$minAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "4"])` - `r sum(inddiff_kids$maxAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "4"])`, `r sum(inddiff_kids$nFemales[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "4"])` girls), and `r sum(inddiff_kids$nTotal[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "5"])` 5-year-olds (mean = `r sum(inddiff_kids$meanAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "5"])` months, SD = `r sum(inddiff_kids$sdAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "5"])`, range = `r sum(inddiff_kids$minAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "5"])` - `r sum(inddiff_kids$maxAgeInMonths[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "5"])`, `r sum(inddiff_kids$nFemales[inddiff_kids$datacollection == "remote - unsupervised" & inddiff_kids$ageInYears == "5"])` girls).
Of these, three families participated twice.
In these cases, we only kept the data sets from the first participation.

@@

Children in our sample grow up in an industrialized, urban Central-European context in a city with approximately 600,000 inhabitants.
They often live in nuclear two-generational families with few household members.
Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.
The median individual monthly net income in the year 2021 was \~ 1,600€ for the city of Leipzig.

Adults were recruited via *Prolific* [@palan2018prolific].
*Prolific* is an online participant recruitment service with a predominantly European and US-American subject pool.
`r inddiff_adults$nTotal` English-speakers with an average age of `r inddiff_adults$meanAge` years (SD = `r inddiff_adults$sdAge`, range = `r inddiff_adults$minAge` - `r inddiff_adults$maxAge`, `r inddiff_adults$nFemales` females) were included.
Participants live in a variety of different countries: the UK, Italy, Spain, Poland, Netherlands, Canada, Australia, Ireland, South Africa, Norway, Portugal, France, Austria, Finland, Greece, Germany, the U.S., Mexico, Chile, Iceland, New Zealand, Czech Republic, Hungary, Latvia, and Switzerland.
In this sample, most participants resided in the United Kingdom (n = 47), South Africa (n = 8), and Portugal (n = 6).
Additional, detailed information can be found in the data set online.
For completing the study, subjects were paid above the fixed minimum wage (on average £10.00 per hour; see Supplements for further detail).

@@

All participants received 15 test trials.
In the box version, we decided to adjust the task difficulty according to the sample: children were presented with five boxes, while adults were presented with eight boxes as possible target locations.

@@

Children showed nearly perfect precision in the first training trial.
As visual access to the target location decreased in the subsequent training trials, imprecision levels increased (see Supplements).
Within test trials, children's imprecision levels did not vary as a function of trial number.
We take this as evidence that (A) children were comfortable touching the screen, (B) children understood the task instructions insofar as they aimed at locating the target, and (C) our experimental design successfully manipulated task difficulty.

@@

For test-retest reliability, we show the association between raw performance scores of the two test days and corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)D, E, I and J.[^4]
See Supplements for reliability estimates by age group.
